{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2015-10-29 paper.tex
Add Justin's feedback, fix typo

The velocity of each joint $J_i$, $1\leq i \leq m$ is defined by a vector of $
\real^{p_i}$, where $p_i$ is the number of DOF of $J_i$. Note that 
the velocity vector does not necessarily have the same dimension as the 
configuration vector.

@@

\subsection {Resolution}
We assume that the direct interpolation between the initial and final configurations contains collisions. An iteration is described as follow:
\begin{equation}\label{eq:iteration-1}
\begin{split}
& \pii =  -H^{-1} \nabla \cost(\xx_i)^{T} \\
& \xx_{i+1} =  \xx_{i} + \alpha_i \pii
\end{split} 
\end{equation}
where $\alpha_i$ is a real valued parameter. Taking $\alpha_i=1$ yields the 
unconstrained minimal cost path, i.e. all waypoints aligned on the straight line 
between $q_0$ and $q_{wp+1}$. Since this solution is in collision, we set 
$\alpha_i = \alpha$ 
where $\alpha$ is a parameter that will be explained in the algorithm section.

@@

In this section, the GB path-optimizer (Algorithm~\ref{algo:gradient}) is described
according to the previous steps definitions. One difficulty here is to handle 
the scalar parameter $\alpha$ determining how much of the computed step $\p$ will 
be traveled through. Typically, we 
chose $\alpha_{init} = 0.2$ or 0.1 to process small steps.

>>>>

The velocity of each joint $J_i$, $1\leq i \leq m$,  belongs to the tangent space of 
the joint configuration space, and is defined by a vector of $\real^{p_i}$, where 
$p_i$ is the number of DOF of $J_i$. Note that
the velocity vector does not necessarily have the same dimension as the 
configuration vector.

@@

\subsection {Resolution}
We assume that the direct interpolation between the initial and final configurations contains collisions. An iteration is described as follow:
\begin{equation}\label{eq:iteration-1}
\begin{split}
& \p_i =  -H^{-1} \nabla \cost(\xx_i)^{T} \\
& \xx_{i+1} =  \xx_{i} + \alpha_i \p_i
\end{split} 
\end{equation}
where $\alpha_i$ is a real valued parameter. Taking $\alpha_i=1$ yields the 
unconstrained minimal cost path, i.e. all waypoints aligned on the straight line 
between $\conf_0$ and $\conf_{wp+1}$. Since this solution is in collision, we set 
$\alpha_i = \alpha_{init}$
where $\alpha_{init}$ is a parameter in interval $[0,1]$.

@@

In this section, the GB path-optimizer (Algorithm~\ref{algo:gradient}) is described
according to the previous steps definitions. One difficulty here is to handle 
the scalar parameter $\alpha$ determining how much of the computed step $\p$ will 
be traveled along. We choose $\alpha_{init} = 0.2$ or 0.1 to process small steps.
